---
title: "Assignment 1 - 2014247"
author: "Oliver Bennett"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r source, echo = FALSE, message = FALSE, results = 'hide', warning = FALSE, cache = TRUE}
source("C:R/EC349 Assignment 1 - 2014247.R")
```
## Methodology

## Business Understanding

## Data Understanding




```{r review histogram, echo=FALSE, cache = TRUE}
# Exploratory Data Analytics
# Histogram for distribution of review stars
hist(merged_data$stars.x, breaks = seq(0.5, 5.5, by = 1), main = "Distribution of Reviews", xlab = "Stars", xaxt = "n")
axis(1, at = 1:5, labels = 1:5)
```

#### Column Names
```{r column names, echo = FALSE, cache = TRUE}
column_names <- colnames(merged_data)
print(column_names)
```



## Data Preparation



| Dataset | Description |
|----|------------------|
| `numeric_df` | Matrix containing only numerical variables. To be used for Ridge and LASSO models |
| `clean_data` | Dataframe containing both numerical and factor type variables with the dependent variable `review_stars` as a numerical type. To be used for OLS and regression tree models |
| `categorical_data` | Same as `clean_data` but `review_stars` is converted to a factor type. To be used for randomly generated reviews and classification tree models |




| Contrasts | Ridge Test MSE | LASSO Test MSE |
|--------|:---------:|:---------:|
| Treatment (dummy) for `review_day_of week`, `review_month`, `review_year` | 0.54380164 | 0.5415141 |
| Polynomial for `review_day_of week`, treatment for `review_month` and `review_year` | 0.5437694 | 0.5414782 |
| Polynomial for `review_day_of week` and `review_month`, treatment for `review_year` | 0.54377904 | <span style="color:blue">0.54139661</span> |
| Polynomial for `review_day_of week`,`review_month` and `review_year` | 0.5437798 | 0.5416604 |




## Modeling


$\hat{\beta}^{OLS} = \arg\min_{\beta} \left\{ \sum_{i=1}^{n} (y_i - x_i^T\beta)^2 \right\}$.

$\hat{\beta}^{Ridge} = \arg\min_{\beta} \left\{ \sum_{i=1}^{n} (y_i - x_i^T\beta)^2 + \lambda \sum_{j=1}^{p} \beta_j^2 \right\}$.

$\hat{\beta}^{LASSO} = \arg\min_{\beta} \left\{ \sum_{i=1}^{n} (y_i - x_i^T\beta)^2 + \lambda \sum_{j=1}^{p} |\beta_j| \right\}$.





## Evaluation


#### MSE Evaluation
| Model | Training MSE | Test MSE |
|:--------:|:---------:|:---------:|
| OLS | 1.176837 | 1.183622 |
| Ridge | 0.5398293 | 0.5437694 |
| <span style="color:blue">LASSO</span> | <span style="color:blue">0.5388094</span> | <span style="color:blue">0.5414782</span> |
| Regression tree | 1.313129 | 1.313515 |
|Randomly generated| 4.723367 | 4.6496 |

#### Prediction Accuracy Evaluation
| Model | Training Accuracy | Test Accuracy |
|:--------:|:---------:|:---------:|
| Randomly generated | 0.2006618 | 0.203 |
|Classification tree| 0.5503822 | 0.5523 |






## Deployment

